A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2020-03-18 paper/paper - revision.Rnw
Minor wording changes

NEW OUTLINE

In the United States, forensic analysis of shoe print evidence in criminal cases is varied and difficult. The process of collecting print evidence from a crime scene is not standardized, and it is often impossible to conduct an individualizing analysis when a print is partial or of low quality. In cases where individualizing characteristics are not considered (estimated at 95\% of cases in the United States according to some experts \footnote{Leslie Hammer, presentation to CSAFE on March 5, 2018}), it is useful to be able to assess the random match probability. In other words, given a questioned shoe print, what is the probability that a randomly selected shoe in the relevant population has a similar tread pattern? Note that this question is distinct from make and model determination since many shoes of different makes and models can still have similar tread patterns (e.g., knockoffs, same models over different years, etc)

>>>>

In the United States, forensic analysis of shoe print evidence in criminal cases is varied and difficult. The process of collecting print evidence from a crime scene is not standardized, and it is often impossible to conduct an individualizing analysis when a print is partial or of low quality. In fact, some experts estimate that 95\% of cases in the United States do not consider individualizing characteristics of shoeprint evidence \footnote{Leslie Hammer, presentation to CSAFE on March 5, 2018}). Even so, in these cases it still may be useful, and much more tractable, to assess the random match probability of the footwear evidence. In other words, given a questioned shoe print, what is the probability that a randomly selected shoe in the relevant population has a similar tread pattern? Note that this question is distinct from make and model determination since many shoes of different makes and models can still have similar tread patterns (e.g., knockoffs, same models over different years, etc).
